Computing solution space properties by generic programming tensor networks \thanks{\funding{...}}

### 2022-03-23 paper/paper.tex
fix the use of ratio

we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lfloor (1-\text{ratio}) \times \alpha(G)\rfloor$ for each instance

@@

While in \Fig{fig:hamming}(b), we observed the multiple peak structure in $3$-regular graphs as the ratio becomes small.

@@

    \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.

>>>>

we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ for each instance

@@

While in \Fig{fig:hamming}(b), we observed the multiple peak structure in $3$-regular graphs as the independent set sizes become large.

@@

    \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.
